Effects of Tunable Hydrophobicity on the Collective Hydrodynamics of Janus Particles under Flows

### 2023-03-30 doc/PRF2022/PRF_main.tex
yny

\section{Results and Discussion}
\label{sec:results}
\begin{figure}[t]
\begin{center}
\includegraphics[width=\textwidth]{S2ESummary.pdf}
\end{center}
\caption{\label{fig:s2esummary}
  Panel (a)--(b) show the average strain increase for bilayer, vesicle
  BL, multilamellar, and striated JP structures under a shear flow and a
  TG flow, respectively. Panel (c)--(d) show the average alignment of
  four JP structures under a shear flow and a TG flow, respectively.
  Each snapshot of panels (e)--(l) contains the configurations of the JP
  structure without ruptures using a specific type of boundary condition
  and the background curves indicate the velocity streamlines.}
\end{figure}
%
We subject the Type I, II, and III JP phases to background flows and
measure their material response. The background flows are a shear flow
\begin{equation}
\label{eq:sh_flow}
\uu_\infty^{\text{sh}}(\xx) = 
\dot\gamma (\ee_y \cdot \mathbf{x})\ee_x,
\end{equation}
and a Taylor-Green (TG) flow
\begin{equation}
\label{eq:tg_flow}
\uu_\infty^{\text{TG}}(\xx) = 
\lambda \dot \gamma \left(
-\cos(\ee_x\cdot\xx/\lambda)\sin(\ee_y\cdot\xx/\lambda)\ee_x
+\sin(\ee_x\cdot\xx/\lambda)\cos(\ee_y\cdot\xx/\lambda)\ee_y\right),
\end{equation}
where the orthonormal vectors $\ee_x$ and $\ee_y$ are the horizontal and
vertical directions, respectively. The shear flow replicates the motion
of a fluid between two parallel, moving plates excluding wall effects.
In TG flow, $\lambda$ controls the size of the $2\pi \lambda \times 2\pi
\lambda$ TG cells. Throughout, we use $\lambda = 2$ nm so that the JP
phases occupy about nine cells.

@@

\begin{figure}[t]
\begin{center}
  \includegraphics[width=\textwidth]{critical_shear_and_cell_size.pdf}
\end{center}
\caption{\label{fig:PramChange}
In panel (a), the relative change in $\dot \gamma_*$ is linear in the
  relative change of the tension parameters $\gamma$ and $M$ with slope
  $1$. Additionally, the relative change in $\dot \gamma_*$ has slope
  $-2$ with respect to the relative change in the length parameters $c$,
  $\rho$, and $\rho_0$. Panels (b)--(e) show the tank-treading
  configuration of a vesicle bilayer the configurations with streamlines
  of a vesicle is in a TG flow at $t=1$ $\upmu$s with $l= 1,2,3,4$,
  respectively. In panel (f),
  inset, the relative enclosed area $A/A_0$
  for the four cases in panels (b)--(e) decays to a steady state.
  The steady-state $A_{\infty}/A_0$ relative area is non-monotonic
  in $\lambda$.} 
%  \todo[inline]{We propose to relate panel (f) to the pressure drops
%  across the JP vesicles. Also, panel (a) should be its own figure, and
%  (b)--(e) can be their own figure, but with darker stream lines. Also,
%  should not be talking about tank treading, but rather about sliding
%  between layers, and how they are affected by the correlation between
%  the bilayer location and the TG cell boundary. This correlation also
%  somehow determines the shape. Can count the number of partial TG cells
%  inside each of the JP bilayer vesicles. (b) has 9 cells, (c) has 2 +
%  4*0.5 cells, (d) has 1 + 4$\epsilon$ cells where $\epsilon < 1/4$, and
%  (e) has 1 cell.}
\end{figure}

>>>>

\section{Results and Discussion}
\label{sec:results}
\begin{figure}[t]
\begin{center}
\includegraphics[width=\textwidth]{S2ESummary.pdf}
\end{center}
\caption{\label{fig:s2esummary}
  Panel (a)--(b) show the average strain increase for bilayer, vesicle
  BL, multilamellar, and striated JP structures under a shear flow and a
  TG flow, respectively. Panel (c)--(d) show the average alignment of
  four JP structures under a shear flow and a TG flow, respectively.
  Each snapshot of panels (e)--(l) contains the configurations of the JP
  structure without ruptures using a specific type of boundary condition
  and the background curves indicate the velocity streamlines.}
\end{figure}
%
We subject the Type I, II, and III JP phases to background flows and
measure their material response. The background flows are a shear flow
\begin{equation}
\label{eq:sh_flow}
\uu_\infty^{\text{sh}}(\xx) = 
\dot\gamma (\ee_y \cdot \mathbf{x})\ee_x,
\end{equation}
and a Taylor-Green (TG) flow
\begin{equation}
\label{eq:tg_flow}
\uu_\infty^{\text{TG}}(\xx) = 
\lambda \dot \gamma \left(
-\cos(\ee_x\cdot\xx/\lambda)\sin(\ee_y\cdot\xx/\lambda)\ee_x
+\sin(\ee_x\cdot\xx/\lambda)\cos(\ee_y\cdot\xx/\lambda)\ee_y\right),
\end{equation}
where the orthonormal vectors $\ee_x$ and $\ee_y$ are the horizontal and
vertical directions, respectively. The shear flow replicates the motion
of a fluid between two parallel, moving plates excluding wall effects.
In TG flow, $\lambda$ controls the size of the $2\pi \lambda \times 2\pi
\lambda$ TG cells. Throughout this section, we use $\lambda = 2$ nm so that the JP
phases occupy about nine cells.

@@

\begin{figure}[t]
\begin{center}
  \includegraphics[width=\textwidth]{critical_shear_and_cell_size.pdf}
\end{center}
\caption{\label{fig:PramChange}
In panel (a), the relative change in $\dot \gamma_*$ is linear in the
  relative change of the tension parameters $\gamma$ and $M$ with slope
  $1$. Additionally, the relative change in $\dot \gamma_*$ has slope
  $-2$ with respect to the relative change in the length parameters $c$,
  $\rho$, and $\rho_0$. Panels (b)--(e) show the tank-treading
  configuration of a vesicle bilayer the configurations with streamlines
  of a vesicle is in a TG flow at $t=1$ $\upmu$s with $\lambda= 1,2,3,4$,
  respectively. In panel (f),
  inset, the relative enclosed area $A/A_0$
  for the four cases in panels (b)--(e) decays to a steady state.
  The steady-state $A_{\infty}/A_0$ relative area is non-monotonic
  in $\lambda$.} 
%  \todo[inline]{We propose to relate panel (f) to the pressure drops
%  across the JP vesicles. Also, panel (a) should be its own figure, and
%  (b)--(e) can be their own figure, but with darker stream lines. Also,
%  should not be talking about tank treading, but rather about sliding
%  between layers, and how they are affected by the correlation between
%  the bilayer location and the TG cell boundary. This correlation also
%  somehow determines the shape. Can count the number of partial TG cells
%  inside each of the JP bilayer vesicles. (b) has 9 cells, (c) has 2 +
%  4*0.5 cells, (d) has 1 + 4$\epsilon$ cells where $\epsilon < 1/4$, and
%  (e) has 1 cell.}
\end{figure}
